Clean - An Abstract Imperative Programming Language and its Theory

### 2019-09-12 C11-BackEnds/Clean/document/root.tex
switch headers
substantially improved documentation

\begin{abstract}
Clean (pronounced as: ``Céline'' [selin]) is based on a simple, abstract execution model for an
imperative target language. ``Abstract'' is understood as contrast to ``Concrete Semantics'';
alternatively, the term ``shallow-style embedding'' could be used.

Clean is based on a ``no-frills'' state-exception monad with the usual definitions of \isa{bind} and
\isa{unit} for the compositional glue of state-based computations. Clean offers conditionals and
loops supporting C-like control-flow operators such as \isa{break} and \isa{return}. The memory
model is fully \HOL{}-typed and based on a construction nesting subsequently extensible
records. Note that the current version only supports monomorphic states and parameters of (directly
recursive) functions.

The design is striving for extreme simplicity. It is geared towards symbolic execution and proven
correct verification tools. The underlying libraries of this package, however, deliberately
restricts itself to the most elementary infrastructure for these tasks. The package is intended to
serve as demonstrator semantic backend for Isabelle/C~\cite{TuongWolff19}, serving as basis for the
test-generation technique described in~\cite{DBLP:conf/tap/Keller18}.
\end{abstract}

@@

\newpage
\section{Appendix : Used Monad Libraries}
\input{MonadSE.tex}

>>>>

\begin{abstract}
Clean  is based on a simple, abstract execution model for an
imperative target language. ``Abstract'' is understood as contrast to ``Concrete Semantics'';
alternatively, the term ``shallow-style embedding'' could be used. It strives for a type-safe
notation of program-variables, an incremental construction of the typed state-space in order 
to facilitate incremental verification and open-world extensibility to new type definitions 
intertwined with the the program definition.

Clean is based on a ``no-frills'' state-exception monad with the usual definitions of \isa{bind} and
\isa{unit} for the compositional glue of state-based computations. Clean offers conditionals and
loops supporting C-like control-flow operators such as \isa{break} and \isa{return}. The state-space
is fully \HOL{}-typed and based on an incremental construction based on extensible
records. Direct recursion of operations is supported.

The design is striving for extreme simplicity. It is geared towards symbolic execution and proven
correct verification tools. The underlying libraries of this package, however, deliberately
restrict themselves to the most elementary infrastructure for these tasks. The package is intended to
serve as demonstrator semantic backend for Isabelle/C~\cite{TuongWolff19}, serving as basis for the
test-generation technique described in~\cite{DBLP:conf/tap/Keller18}.
\end{abstract}

@@

\newpage
\chapter{Appendix : Used Monad Libraries}
\input{MonadSE.tex}
